sensiAnPaper1All

### 2015-07-14 sensiAnPaper1All.Rmd
add 20% better calculations

```{r}
  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_100_4.rda'))
  load(file=paste0(outFolder,'listOutI1_100_4.rda'))
  load(file=paste0(outFolder,'listOutI2_100_4.rda'))

@@

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #the mixture one looks superficially similar to the individual ones superimposed
  #x11()
#   plotallele.freq.andy(listOutMix)
#   #x11()
#   plotallele.freq.andy(listOutI1)
#   #x11()
#   plotallele.freq.andy(listOutI2)

@@

>>>>

```{r}
  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_1000.rda'))
  load(file=paste0(outFolder,'listOutI1_1000.rda'))
  load(file=paste0(outFolder,'listOutI2_1000.rda'))

@@

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #x11()
#   plotallele.freq.andy(listOutMix)
#   #x11()
#   plotallele.freq.andy(listOutI1)
#   #x11()
#   plotallele.freq.andy(listOutI2)

@@

### finding when mixtures are >20% better
### repeating calculation of the difference between sequential & mixture scenarios
```{r}

  ## is mix1 better than sequential ?
  #T/F
  resistBetterMix1SeqBoolean20 <- resistPointsMix1 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix1Seq20 <- plyr::aaply(resistBetterMix1SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix1Seq20) <- gsub('gen','betterMix1Seq20', rownames(resistBetterMix1Seq20))

  rowSums(resistBetterMix1Seq20)/ncol(resistBetterMix1Seq20)
  #1000runs
 #betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
 #                 0.136                  0.175                  0.173

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix2SeqBoolean20 <- resistPointsMix2 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix2Seq20 <- plyr::aaply(resistBetterMix2SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix2Seq20) <- gsub('gen','betterMix2Seq20', rownames(resistBetterMix2Seq20))

  rowSums(resistBetterMix2Seq20)/ncol(resistBetterMix2Seq20)  
  #1000runs
#  betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
#                  0.241                  0.326                  0.313

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix3SeqBoolean20 <- resistPointsMix3 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix3Seq20 <- plyr::aaply(resistBetterMix3SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix3Seq20) <- gsub('gen','betterMix3Seq20', rownames(resistBetterMix3Seq20))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix3Seq20)/ncol(resistBetterMix3Seq20)
  #1000runs
#  betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
#                  0.672                  0.560                  0.488
